Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2024-09-25 whittaker.tex
Fixing tiny typos

We begin by defining different bases of~$\g$. Start with the following basis:
$$
E_\R=\begin{pmatrix}0&i\\0&0\end{pmatrix},
F_\R=\begin{pmatrix}0&0\\-i&0\end{pmatrix},
H_\R=\begin{pmatrix}1&0\\0&-1\end{pmatrix}
$$
These elements satisfy the standard $SL(2)$ commutation relations: 
\[ [E_\R, F_\R] = H_\R, \quad [H_\R, E_\R] = 2E_\R, \quad [H_\R, F_\R] = -2F_\R. \]

@@

Set $g=\frac 1{\sqrt 2}\begin{pmatrix}1&i\\i&1
\end{pmatrix}$, and take $E_\theta,F_\theta,H_\theta$ be the conjugates of $E_\R,F_\R,H_\R$ by~$g$:
$$
E_\theta=\frac12\begin{pmatrix}1&i\\i&-1\end{pmatrix},
F_\theta=\frac12\begin{pmatrix}1&-i\\-i&-1\end{pmatrix},
H_\theta=\begin{pmatrix}0&-i\\i&0\end{pmatrix},
$$
These also satisfy the standard $SL(2)$ commutation relations; $E_\theta,F_\theta$ are in the $-1$-eigenspace of $\theta$; 
and  $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.

@@

First let us compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
\end{pmatrix})$ for $k\in \Z_{\ne 0}$.
Here we are taking the real asymptotic cone; since $kH_\theta\in i\g(\R)$ this is a subset of $i\g(\R)$. 
Taking the limit as $x\rightarrow \infty$ in 
$$
\begin{pmatrix}
x&0\\0&\frac 1x
\end{pmatrix}
\begin{pmatrix}0&-ik\\ik&0
\end{pmatrix}\begin{pmatrix}
\frac 1x&0\\0&x
\end{pmatrix}=
\begin{pmatrix}0&-ikx^2\\\frac{ik}{x^2}&0
\end{pmatrix}
$$
we see
$$
\AC(G(\R)\cdot kH_\theta)=-G(\R)\cdot\sgn(k)E_\R.
$$
Now we carry out this computation over to $i\g(\R)^*$:
$$
\begin{aligned}
\AC(G(\R)\cdot\lambda_{ik})&=\AC(G(\R)\cdot kH_\theta^*)\\
&=\psi_c(\AC(G(\R)\cdot \psi_c\inv(kH_\theta^*))\\
&=\psi_c(-G(\R)\cdot\sgn(\frac k{2c})E_\R)\\
&=-G(\R)\cdot\sgn(\frac k{2c})cF_\R^*\\
&=-G(\R)\cdot\sgn(k)F_\R^*\\
&=G(\R)\cdot(-\sgn(k)E_\R^*).
\end{aligned}
$$
In the last line we used the fact that $E_\R^*,F_\R^*$ are $G(\R)$-conjugate.
Note that $c$ disappeared from the end result, as expected.

@@

We apply Lemma \ref{l:AV}. It is easy to see
$$
F_{\pi(\lambda_{ik})}=
\begin{cases} F_\theta&\text{ if $k>0$;}\\
  E_\theta& \text{ if $k<0$.}
\end{cases}
$$
Recall that in Section \ref{s:AV} we use the isomorphism $\psi$ defined using the Killing form $\kappa_4$, which satisfies
$\psi(F_\theta)=4E^*_\theta, \psi(E_\theta)=4F^*_\theta$. 
Therefore
\begin{equation}
  \label{e:AV}
\AV(\pi(\lambda_{ik}))=
\begin{cases}K\cdot E_\theta^*&k>0\\
  K\cdot F_\theta^*&k<0\\
\end{cases}
\end{equation}

@@

Suppose $\pi=\pi(\lambda_{ik})$. First assume $k>0$ and compute
$$
\begin{aligned}
\KS(\AV(\pi))&=  \KS(K\cdot E_\theta^*)\quad \text{by \eqref{e:AV}}\\
&=  \psi_c(\KS(K\cdot \psi_c\inv (E_\theta^*)))\\
  &=  \psi_c(\KS(K\cdot \frac 1c F_\theta))\\
&=\psi_c(G(\R)\cdot \frac 1c(-E_\R))\quad\text{(by \eqref{e:KS})}\\
&=  G(\R)\cdot \psi_c(\frac{-1}c F_\R))\\
&=G(\R)\cdot (-E_\R^*)\\
&=\WF(\pi)\quad \text{(by \ref{e:WF})}
\end{aligned}
$$
which agrees with 
Proposition \ref{Sekiguchi_result}. If $k<0$, replace $E_\theta^*$ with $F_\theta^*$, and conclude $\KS(\AV(\pi))=G(\R)\cdot E_\R^*$, in accordance with
Proposition \ref{Sekiguchi_result}.

>>>>

We begin by defining different bases of~$\g$. Start with the following basis:
$$
E_\R=\begin{pmatrix}0&i\\0&0\end{pmatrix},\quad 
F_\R=\begin{pmatrix}0&0\\-i&0\end{pmatrix},\quad
H_\R=\begin{pmatrix}1&0\\0&-1\end{pmatrix}.
$$
These elements satisfy the standard $SL(2)$ commutation relations: 
\[ [E_\R, F_\R] = H_\R, \quad [H_\R, E_\R] = 2E_\R, \quad [H_\R, F_\R] = -2F_\R. \]

@@

Set $g=\frac 1{\sqrt 2}\begin{pmatrix}1&i\\i&1
\end{pmatrix}$, and take $E_\theta,F_\theta,H_\theta$ be the conjugates of $E_\R,F_\R,H_\R$ by~$g$:
$$
E_\theta=\frac12\begin{pmatrix}1&i\\i&-1\end{pmatrix}, \quad
F_\theta=\frac12\begin{pmatrix}1&-i\\-i&-1\end{pmatrix},\quad
H_\theta=\begin{pmatrix}0&-i\\i&0\end{pmatrix}.
$$
These also satisfy the standard $SL(2)$ commutation relations; $E_\theta,F_\theta$ are in the $-1$-eigenspace of $\theta$; 
and  $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.

@@

First let us compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
\end{pmatrix})$ for $k\in \Z_{\ne 0}$.
Here we are taking the real asymptotic cone; since $kH_\theta\in i\g(\R)$ this is a subset of $i\g(\R)$. 
Taking the limit as $x\rightarrow \infty$ in 
$$
\begin{pmatrix}
x&0\\0&\frac 1x
\end{pmatrix}
\begin{pmatrix}0&-ik\\ik&0
\end{pmatrix}\begin{pmatrix}
\frac 1x&0\\0&x
\end{pmatrix}=
\begin{pmatrix}0&-ikx^2\\\frac{ik}{x^2}&0
\end{pmatrix}
$$
we see
$$
\AC(G(\R)\cdot kH_\theta)=-G(\R)\cdot\sgn(k)E_\R.
$$
Now we carry this computation over to $i\g(\R)^*$:
$$
\begin{aligned}
\AC(G(\R)\cdot\lambda_{ik})&=\AC(G(\R)\cdot kH_\theta^*)\\
&=\psi_c(\AC(G(\R)\cdot \psi_c\inv(kH_\theta^*))\\
&=\psi_c(-G(\R)\cdot\sgn(\frac k{2c})E_\R)\\
&=-G(\R)\cdot\sgn(\frac k{2c})cF_\R^*\\
&=-G(\R)\cdot\sgn(k)F_\R^*\\
&=G(\R)\cdot(-\sgn(k)E_\R^*).
\end{aligned}
$$
In the last line we used the fact that $E_\R^*,F_\R^*$ are $G(\R)$-conjugate.
Note that $c$ disappeared from the end result, as expected.

@@

We apply Lemma \ref{l:AV}. It is easy to see
$$
F_{\pi(\lambda_{ik})}=
\begin{cases} F_\theta&\text{ if $k>0$;}\\
  E_\theta& \text{ if $k<0$.}
\end{cases}
$$
Recall that in Section \ref{s:AV} we use the isomorphism $\psi$ defined using the Killing form $\kappa_4$, which satisfies
$\psi(F_\theta)=4E^*_\theta, \psi(E_\theta)=4F^*_\theta$. 
Therefore
\begin{equation}
  \label{e:AV}
\AV(\pi(\lambda_{ik}))=
\begin{cases}K\cdot E_\theta^*&k>0;\\
  K\cdot F_\theta^*&k<0.\\
\end{cases}
\end{equation}

@@

Suppose $\pi=\pi(\lambda_{ik})$. First assume $k>0$ and compute
$$
\begin{aligned}
\KS(\AV(\pi))&=  \KS(K\cdot E_\theta^*)\quad \text{by \eqref{e:AV}}\\
&=  \psi_c(\KS(K\cdot \psi_c\inv (E_\theta^*)))\\
  &=  \psi_c(\KS(K\cdot \frac 1c F_\theta))\\
&=\psi_c(G(\R)\cdot \frac 1c(-E_\R))\quad\text{(by \eqref{e:KS})}\\
&=  G(\R)\cdot \psi_c(\frac{-1}c F_\R))\\
&=G(\R)\cdot (-E_\R^*)\\
&=\WF(\pi)\quad \text{(by \eqref{e:WF})}
\end{aligned}
$$
which agrees with 
Proposition \ref{Sekiguchi_result}. If $k<0$, replace $E_\theta^*$ with $F_\theta^*$, and conclude $\KS(\AV(\pi))=G(\R)\cdot E_\R^*$, in accordance with
Proposition \ref{Sekiguchi_result}.
